Optimal Fitting of Planar Curves to Prescribed Constraints

### 2013-08-11 idp/documentation/paper.tex
added illustration for spiro spline design tools

>>>>

				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{../resources/usability_spiro.pdf}
					\caption{Usability Analysis of Spiro Splines}
					\label{figure:usability_spiro}
				\end{figure}

				% TODO: improve example index numbers
				Figure \ref{figure:usability_spiro} illustrates some of these issues by showing some examples of Spiro splines as they appear in common design tools. Control points are displayed as filled dots.

				Example 1 shows a shape that is in principle well-suited for being represented by parts of the Euler spiral. Unfortunately, describing the curve using Spiro splines still requires many control points. In contrast to the corresponding example in section \ref{section:common_design_tools_bézier_splines}, the curve in this example is close to a perfect spiral an thus does not match the source image perfectly. Additional control points would have to be added in order to approximate the imperfect spiral in the source image better.

				Example 2 shows how some shapes can be described using Spiro splines by placing only very few control points. In this case, the shape consists of a circle arc with low curvature (segment a), a segment of linearly increasing curvature (segment b) and finally a circle arc with high curvature (segment c). This shape can be described conveniently using a Spiro spline with just 4 control points.

				Unfortunately, as can be seen in example 3, this scenario does not handle modifications very well. For instance, increasing the curvature of segment c has to be done indirectly by moving a control point. Unfortunately, in this case, this also changes the direction of the curve at that point, such that additional modifications would be needed to correct this. The change also adversely affects segment a, since the curvature there was not specified directly but instead relied on the rather fragile configuration of the 4 control points.
